New lower bounds for Schur and weak Schur numbers

### 2021-04-07 article/schur.tex
inequality on SE

\begin{theorem}
	Let \(n, k \in \mathbb{N}^*\), we have \\
	\[ S(n+k) \geqslant SE_+(k+1)S(n) \]
\end{theorem}

Using a SAT solvers, we are able to exhibit adequate Schur partitions, i.e satisfying \(SE_+\) constraint, 
hence providing lower bound on \(SE_+\). We refer to such partition as \textit{templates}. Moreover, when using 
a template in the above formula, it is possible to get an additive constant. We seek templates providing "affine"
inequalities : \(aS(n+k) + b \) where \(a\) is a lower bound for \(SE_+(k+1)\). Further details can be found in the \hyperref[SAT]{SAT section}.
Here are the best inequalities on Schur numbers so far :
\[ S(n+1) \geq 3S(n) + 1 \\
 S(n+2) \geq 9S(n) + 4 \\
 S(n+3) \geq 33S(n) + 6 \\
 S(n+4) \geq 111S(n) + 43 \\
 S(n+5) \geq 380S(n) + 148 \\
 S(n+6) \geq 1140S(n) + 528 \]

>>>>

\begin{theorem}
	Let $(n,k), (r,s) \in (\mathbb{N}^*)^2$. If there exists a \(SF\)-template of $k+1$ colors and lenght \(r\),
	and a partition of $n$ sum-free subsets of $[\![1,s]\!]$ then there exists a partition of $n+k$ sum-free subsets of $[\![1,rs]\!]$
\end{theorem}

Setting $r = SE_+(k+1)$ and $s = S(n)$ yields the following corollary.

\begin{corollary}
	Let \(n, k \in \mathbb{N}^*\), we have \\
	\[ S(n+k) \geqslant SE_+(k+1)S(n) \]
\end{corollary}

Using a SAT solvers, we are able to exhibit SF-template,
hence providing lower bound on \(SE_+\). Moreover, when using 
a SF-template in the above formula, it is possible to get an additive constant. We seek templates providing "affine"
inequalities : \(aS(n+k) + b \) where \(a\) is a lower bound for \(SE_+(k+1)\). Further details can be found in the \hyperref[SAT]{SAT section}.
Here are the best inequalities on Schur numbers so far :
\[ S(n+1) \geqslant 3S(n) + 1 \]
\[ S(n+2) \geqslant 9S(n) + 4 \]
\[ S(n+3) \geqslant 33S(n) + 6 \]
\[ S(n+4) \geqslant 111S(n) + 43 \]
\[ S(n+5) \geqslant 380S(n) + 148 \]
\[ S(n+6) \geqslant 1140S(n) + 528 \]

The first inequality comes from the original Schur's paper \hyperlink{label1}{\textbf{[1]}}. The second and third ones were found by Rowley (reference nécessaire), 
and the other ones are new. \\

We also have a similar theorem where only \(SE_+\) is involved.

\begin{theorem}
	Let $(n,k), (r,s) \in (\mathbb{N}^*)^2$. If there exists a \(SF\)-template of $k+1$ colors and lenght \(r\),
	and \(SF\)-template of \(n\) color and lenght \(s\), then there exists \(SF\)-template of \((n+k)\) and lenght \(rs\).
\end{theorem}

And the associated inequality :

\begin{corollary}
	Let \(n, k \in \mathbb{N}^*\), we have \\
	\[ SE_+(n+k) \geqslant SE_+(k+1)SE_+(n) \]
\end{corollary}
